%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Research Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------


\begin{cventries}




%---------------------------------------------------------



  \cventry
    {Research Associate at \href{https://www.frc.ri.cmu.edu/}{Field Robotics Center}} % Job title
    {\href{https://www.ri.cmu.edu/}{Carnegie Mellon University}} % Organization
    {Pittsburgh, PA} % Location
    {Nov. 2017 - present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
      	\item \textbf{Developing Planning Software for multi-agent air/ground robots for DARPA Subterranean Challenge:} \begin{flushright} {\color{awesome} Adviser: Dr. Sebastian Scherer} \end{flushright}
		\begin{itemize}
			\item Developing simulation environmentin gazebo and implementing Global and Local Trajectory Planner in ROS.
		\end{itemize}	
		\item \textbf{Successfully deployed first of its kind, autonomous inspection system for decommissioning
uranium enrichment facilities} \begin{flushright} {\color{awesome} Adviser: Prof. William (Red) Whittaker} \end{flushright}
		\begin{itemize}
			\item Leading Autonomy team  for state estimation, 3D Perception and state machine.
			\item Control/ROS developer for attitude and position control.
		\end{itemize}
		\item \textbf{Developing Software/Hardware for Moon Rover Robot} \begin{flushright} {\color{awesome} Adviser: Prof. William (Red) Whittaker} \end{flushright}
		\begin{itemize}
			\item Developing Software/Hardware of a custom designed light weighted LiDar to construct a 3D point cloud of environment
		\end{itemize}
      \end{cvitems}
    }





%---------------------------------------------------------

  \cventry
    {Research Assistant at NICEST Lab} % Job title
    {\href{http://www.uic.edu}{University of Illinois at Chicago}} % Organization
    {Chicago, IL} % Location
    {Aug. 2015 - Nov 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
		\item \textbf{Designing a fully integrated radar and communication system} \begin{flushright} {\color{awesome} Adviser: Dr. Besma Smida} \end{flushright}
		\begin{itemize}
				\item Proposing, Formulating and Designing the integrated radar and communication system using pilot symbols
		\end{itemize}
		\item \textbf{Optimizing Pilot Overhead for Ultra-Reliable Short-Packet Transmission} \begin{flushright} {\color{awesome} Adviser: Dr. Besma Smida} \end{flushright}
		\begin{itemize}
				\item Formulating and Optimizing wireless communication systems for short packet communication.
		\end{itemize}				      
      \end{cvitems}
    }





%---------------------------------------------------------
  \cventry
    {Research Assistant at Computer Vision Lab} % Job title
    {\href{http://www.sharif.ir/web/en}{Sharif University Of Technology}} % Organization
    {Tehran, Iran} % Location
    {Nov. 2014 - Feb. 2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
			\item \textbf{Designing and Implementing an autonomous home assistant robot for participating in AUT-CUP competitions} \begin{flushright} {\color{awesome} Adviser: Dr. Mansour Jamzad} \end{flushright}
			\begin{itemize}
					\item Design and Implementation of an at-Home robot (Electromechanical Platform, Motion planning, Control)
			\end{itemize}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Research Assistant at Computer Vision Lab} % Job title
    {\href{http://aut.ac.ir/aut/}{Tehran Polytechnic University}} % Organization
    {Tehran, Iran} % Location
    {Jan. 2015 - Jul. 2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item \textbf{Developing an autonomous home assistant  Robot for ROBOCUP 2015 (Joao Pessoa, Brazil)} \begin{flushright} {\color{awesome} Adviser: Dr. Saeed Shiry} \end{flushright}
        \begin{itemize}
        \item ROS/OpenCV developer for object detection
        \end{itemize}
      \end{cvitems}
    }

%---------------------------------------------------------
%  \cventry
%    {Research Assistant at Telecommunications Lab} % Job title
%    {\href{http://en.sbu.ac.ir/sitepages/home.aspx}{Shahid Beheshti University}} % Organization
%    {Tehran, Iran} % Location
%    {Sep. 2013 - Dec. 2013} % Date(s)
%    {
%      \begin{cvitems} % Description(s) of tasks/responsibilities
%        \item Research on optimizing Power Line Communication Systems (PLC) with OFDM Modulation, Advisor: Prof. Afjei.
%        \begin{itemize}
%        		\item Simulating MMSE channel estimation method in PLC with OFDM Modulation(Using MATLAB)
%        		\item Simulating the same channel over different modulations (QAM, FSK, PSK) and comparing with OFDM
%        \end{itemize}
%      \end{cvitems}
%    }


\end{cventries}
